Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-17 doc/manuscript/manuscript.Rmd
Add repeat motif to locus table stats
I also removed the average values because it only
made sense for three of the numbers. Now all but
table 1 are reproducible.

--------------------------------------------
Locus  Range    No. alleles    *h*  Evenness 
------ ------- ------------ ------ ---------
5-2    318-324            4   0.45      0.62

6-2    483-495            3   0.64      0.95

7-2    158-174            7   0.73      0.76

8-3    244-270            7   0.74      0.79

9-2    360-382            9   0.35      0.41

12-2   214-222            5   0.58      0.78

17-3   342-363            7   0.55      0.53

20-3   280-282            2   0.05      0.42

55-4   153-216           10   0.72      0.66

110-4  370-386            5   0.76      0.91

114-4  339-416           10   0.83      0.80

mean   153-495         6.27   0.58      0.69

--------------------------------------------

Table: (\#tab:locus-stats) Allelic diversity on full data set at loci used in this study. *h* = Nei's Gene Diversity [@nei1978estimation].

>>>>

```{r , echo = FALSE, warning = FALSE, message = FALSE, results = "asis"}
suppressPackageStartupMessages(library("tidyverse"))
loc_columns <- cols(
  Locus = col_character(),
  Range = col_character(),
  Repeats = col_double(),
  allele = col_integer(),
  Hexp = col_double(),
  Evenness = col_double()
)
loc_table <- readr::read_csv("../../results/tables/locus-table.csv", 
                             col_types = loc_columns,
                             col_names = TRUE)
loc_table %>%
  mutate(allele = round(allele, 2)) %>%
  mutate(Repeats = case_when(
    Repeats <= 2 ~ "di-",
    Repeats <= 3 ~ "tri-",
    Repeats <= 4 ~ "tetra-",
    Repeats <= 5 ~ "penta-",
    Repeats <= 6 ~ "hexa-"
  )) %>%
  rename(`*h*` = Hexp) %>%
  rename(`No. alleles` = allele) %>%
  rename(`Repeat Motif` = Repeats) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>%
  huxtable::set_number_format(huxtable::everywhere, 3:4, 0) %>%
  huxtable::set_number_format(huxtable::everywhere, 5:6, 2) %>%
  huxtable::set_align(huxtable::everywhere, 2:6, "right") %>%
  huxtable::set_col_width(c(0.06, 0.07, 0.11, 0.1, 0.05, 0.075)) %>%
  huxtable::print_md(max_width = 61)

Amean <- mean(loc_table$allele)
Hmean <- mean(loc_table$Hexp)
Emean <- mean(loc_table$Evenness)
```

Table: (\#tab:locus-stats) Allelic diversity on full data set at loci used in this study. *h* = Nei's Gene Diversity [@nei1978estimation]. Average *h* = `r signif(Hmean, 3)`, average Evenness = `r signif(Emean, 3)`, average no. alleles = `r signif(Amean, 3)`
